Active Learning for Level Set Estimation

### 2013-03-19 msthpres.tex
LSE algorithm

@@

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<16->{\Large\color{green!70!black}\checkmark}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.5in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.5in]{figures/voned_cl_00}
\includegraphics<5>[width=3.5in]{figures/voned_cl_01}
\includegraphics<6>[width=3.5in]{figures/voned_cl_10}
\includegraphics<7>[width=3.5in]{figures/voned_cl_11}
\includegraphics<8>[width=3.5in]{figures/voned_cl_20}
\includegraphics<9>[width=3.5in]{figures/voned_cl_21}
\includegraphics<10>[width=3.5in]{figures/voned_cl_30}
\includegraphics<11>[width=3.5in]{figures/voned_cl_31}
\includegraphics<12>[width=3.5in]{figures/voned_cl_40}
\includegraphics<13->[width=3.5in]{figures/voned_cl_41}
\end{center}
\end{frame}

>>>>

%%
\usepackage{xspace}
\usepackage{msthpres}
\newcommand{\gpucb}{\textsf{GP-UCB}\xspace}
\newcommand{\gpbucb}{\textsf{GP-BUCB}\xspace}
\newcommand{\acl}{\textsf{LSE}\xspace}
\newcommand{\fullacl}{Level Set Estimation\xspace}
\newcommand{\iacl}{\textsf{LSE\textsubscript{imp}}\xspace}
\newcommand{\bacl}{\textsf{LSE\textsubscript{batch}}\xspace}
\newcommand{\ibacl}{\textsf{LSE\textsubscript{imp-batch}}\xspace}
\newcommand{\str}{\textsf{STR}\xspace}
\newcommand{\istr}{\textsf{STR\textsubscript{imp}}\xspace}
\newcommand{\bstr}{\textsf{STR\textsubscript{batch}}\xspace}
\newcommand{\rstr}{\textsf{STR\textsubscript{rank}}\xspace}
\newcommand{\var}{\textsf{VAR}\xspace}
%%

@@

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<24->{\Large\color{green!70!black}\checkmark}
\uncover<16->{
\begin{itemize}
\item<16-> Pick among the yet unclassified.
\item<17-> Doesn't really matter which!\\
           \uncover<18->{(e.g. max. variance, }\uncover<19->{max. ambiguity}\uncover<23->{, or even random)}
\end{itemize}}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.5in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.5in]{figures/voned_cl_00}
\includegraphics<5>[width=3.5in]{figures/voned_cl_01}
\includegraphics<6>[width=3.5in]{figures/voned_cl_10}
\includegraphics<7>[width=3.5in]{figures/voned_cl_11}
\includegraphics<8>[width=3.5in]{figures/voned_cl_20}
\includegraphics<9>[width=3.5in]{figures/voned_cl_21}
\includegraphics<10>[width=3.5in]{figures/voned_cl_30}
\includegraphics<11>[width=3.5in]{figures/voned_cl_31}
\includegraphics<12>[width=3.5in]{figures/voned_cl_40}
\includegraphics<13-19>[width=3.5in]{figures/voned_cl_41}
\includegraphics<20>[width=3.5in]{figures/voned_cl_41_amb_0}
\includegraphics<21>[width=3.5in]{figures/voned_cl_41_amb_1}
\includegraphics<22->[width=3.5in]{figures/voned_cl_41_amb_2}
\end{center}
\end{frame}

\definecolor{c1}{RGB}{255,255,255}
\definecolor{c2}{RGB}{27,161,226}
\definecolor{c6}{RGB}{140,191,38}
\definecolor{c4}{RGB}{240,150,9}
\definecolor{c5}{RGB}{255,255,255}
\definecolor{c3}{RGB}{230,113,184}
%\colorlet{c1}{cyan}
%\colorlet{c2}{magenta}
%\colorlet{c3}{red}
%\colorlet{c4}{green}
%\colorlet{c5}{yellow}

\begin{frame}
\begin{columns}[t]
\column{0.5\textwidth}
{\footnotesize
\begin{algorithmic}[1]
  \REQUIRE sample set $D$, GP prior ($\mu_0 = 0$, $k$, $\sigma_0$),\\
           \hspace{1.35em}threshold value $h$, accuracy parameter $\epsilon$
  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
  \uncover<2->{
  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
  %\LET{$L_0$}{$\varnothing$}
  %\LET{$U_0$}{$D$}
  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
  \CLET{c1}{$t$}{1}
  }
  \uncover<3->{
  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
    }
    %\LET{$H_t$}{$H_{t-1}$}
    %\LET{$L_t$}{$L_{t-1}$}
    %\LET{$U_t$}{$U_{t-1}$}
    \uncover<4->{
    \CFORALL{c2}{$\*x \in U_{t-1}$}
      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
      \CENDIF{c2} \label{lin:class2}
    \CENDFOR{c2}
    }
    \uncover<5->{
    \CLET{c3}{$\*x_t$}{$\argmax_{\*x \in U_t}(a_t(\*x))$} \label{lin:sel1}
    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
    }
    \uncover<6->{
    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, for all $\*x \in U_t$ \label{lin:inf}
    }
    \uncover<3->{
    \CLET{c6}{$t$}{$t + 1$}
  \CENDWHILE{c6}
  }
  \uncover<2->{
  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
  }
\end{algorithmic}
}
\column{0.5\textwidth}
\begin{center}
The Level Set Estimation (\acl) algorithm
\end{center}
\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
\only<6>{$\leftarrow$ {\small update GP estimate}}
\only<7->{
\vspace{3pt}
\begin{itemize}
\only<7->{
\item Monotonicity of
\begin{enumerate}
\item confidence intervals
\item classification
\end{enumerate}
}
\vspace{0em}
\only<8->{
\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
      (trades off sampling cost for accuracy)
}
\end{itemize}
}
\begin{center}
\includegraphics<8->[width=2in]{figures/voned_cl_41_eps}
\end{center}
\end{columns}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\

\only<1>{\color{white}\small{$t = 0$\\}}
\only<2>{\small{$t = 0$\\}}
\only<3>{\small{$t = 20$\\}}
\only<4>{\small{$t = 40$\\}}
\only<5>{\small{$t = 60$\\}}
\only<6>{\small{$t = 80$\\}}
\only<7>{\small{$t = 100$\\}}
\only<8>{\small{$t = 120$\\}}
\only<9>{\small{$t = 140$\\}}
\only<10>{\small{$t = 160$\\}}
\only<11>{\small{$t = 180$\\}}
\only<12>{\small{$t = 200$\\}}
%\only<13>{\small{$t = 220$\\}}
%\only<14>{\small{$t = 240$\\}}
\only<13>{\small{$t = 260$\\}}
%\only<16>{\small{$t = 280$\\}}
%\only<17>{\small{$t = 300$\\}}
%\only<18>{\small{$t = 320$\\}}
%\only<19>{\small{$t = 340$\\}}
\only<14>{\small{$t = 354$\\}}

\hspace{-1.9em}
\color{white}
\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
\color{black}
\includegraphics<2>[width=3.78in]{figures/limno_bgape_class_0}
\includegraphics<3>[width=3.78in]{figures/limno_bgape_class_20}
\includegraphics<4>[width=3.78in]{figures/limno_bgape_class_40}
\includegraphics<5>[width=3.78in]{figures/limno_bgape_class_60}
\includegraphics<6>[width=3.78in]{figures/limno_bgape_class_80}
\includegraphics<7>[width=3.78in]{figures/limno_bgape_class_100}
\includegraphics<8>[width=3.78in]{figures/limno_bgape_class_120}
\includegraphics<9>[width=3.78in]{figures/limno_bgape_class_140}
\includegraphics<10>[width=3.78in]{figures/limno_bgape_class_160}
\includegraphics<11>[width=3.78in]{figures/limno_bgape_class_180}
\includegraphics<12>[width=3.78in]{figures/limno_bgape_class_200}
%\includegraphics<13>[width=3.78in]{figures/limno_bgape_class_220}
%\includegraphics<14>[width=3.78in]{figures/limno_bgape_class_240}
\includegraphics<13>[width=3.78in]{figures/limno_bgape_class_260}
%\includegraphics<16>[width=3.78in]{figures/limno_bgape_class_280}
%\includegraphics<17>[width=3.78in]{figures/limno_bgape_class_300}
%\includegraphics<18>[width=3.78in]{figures/limno_bgape_class_320}
%\includegraphics<19>[width=3.78in]{figures/limno_bgape_class_340}
\includegraphics<14>[width=3.78in]{figures/limno_bgape_class_354}
\end{center}
\end{frame}
